Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-23 paper/tex/sections/comparisons.tex
update comparisons based on new info on simple mw

\paragraph{\citet{Lau+2020}} focussed on the number of Galactic NSNS binaries that could be detected by LISA. Their study uses the same population synthesis code, COMPAS, as this work, though an earlier version. Despite this, their study finds a much larger number of detections. They make several different physical assumptions in their population synthesis, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN. However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.~\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}) and so this is unlikely to entirely account for our differences. It is also important to highlight that COMPAS has had many improvements and bug fixes since \citet{Vigna-Gomez+2018} (which contains the simulations used by \citet{Lau+2020}) and these could have affected the formation rate of NSNSs.
%
It is also possible that the remaining difference between our results is due to way in which we simulate the Milky Way. \citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we used to estimate how impactful the choice of MW model was in Appendix~\ref{sec:mw_changes}. We find that this simpler model for the Milky Way could result in an overestimate of the NSNS detection rate and so this may explain the discrepancy between our results. \citet{Lau+2020} additionally only uses a single metallicity rather than the two used in \citet{Breivik+2020} and so this effect could be even stronger as their results will have no contribution from lower metallicity systems.

\paragraph{\citet{Breivik+2020}} introduced the population synthesis code COSMIC and presented detections for many different DCO types in LISA using this code. They find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission. They make many different physical assumptions, the most notable being that \citet{Breivik+2020} assume the optimistic CE scenario and that case BB mass transfer is always unstable. Thus it would be more prudent to compare to our results from model \modCaseBBOpt{} in which we find 154, 148 and 18 detections respectively. \todo{I am in the process of running some sims using Katie's MW model to compare more easily, will update soon}%Thus the NSNS rate is consistent but we find higher rates for the BHBHs and BHNSs. These differences are likely due to using a different population synthesis code (COSMIC) and using a different model for the Milky Way, particularly the assumptions of two fixed metallicities.

\paragraph{\citet{Shao+2021}} most recently investigated the detectability binaries containing BHs in LISA using BSE and a relatively simple model for the Milky Way (assuming a uniform flat disc, constant star formation and a single metallicity). They assume that kicks for NSs formed through ECSN are slightly higher than our work ($50 \unit{km}{s^{-1}}$ instead of $30 \unit{km}{s^{-1}}$). This may account for their particular low BHNS rate (as the binaries would be more likely to disrupt), which is a factor of 20 lower than ours, but we expect their assumption of the optimistic CE scenario, reduced Wolf-Rayet winds and lower SNR detection threshold would offset this. It is however difficult to compare further due to our vastly different assumptions about the Milky Way, particularly their assumption of only solar metallicity which eliminates any contribution from low metallicity systems.

>>>>

\paragraph{\citet{Lau+2020}} focussed on the number of Galactic NSNS binaries that could be detected by LISA. Their study uses the same population synthesis code, COMPAS, as this work, though an earlier version. Despite this, their study finds a much larger number of detections. They make several different physical assumptions in their population synthesis, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN. However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.~\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}) and so this is unlikely to entirely account for our differences. It is also important to highlight that COMPAS has had many improvements and bug fixes since \citet{Vigna-Gomez+2018} (which contains the simulations used by \citet{Lau+2020}) and these could possibly have affected the formation rate of NSNSs.
%
It is most likely the remaining difference between our results is due to way in which we simulate the Milky Way. \citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we used to estimate how impactful the choice of MW model was in Appendix~\ref{sec:mw_changes}. We find that this simpler model for the Milky Way could result in an overestimation of the NSNS detection rate by at least a factor of two and so this may explain the discrepancy between our results. \citet{Lau+2020} additionally only uses a single metallicity rather than the two used in \citet{Breivik+2020} and so this effect could be even stronger as their results will have no contribution from lower metallicity systems.

\paragraph{\citet{Breivik+2020}} introduced the population synthesis code COSMIC and presented detections for many different DCO types in LISA using this code. They find that LISA will detect 93 BHBHs, 33 BHNSs and 8 NSNSs in the Milky Way over a 4 year mission. \citet{Breivik+2020} make many different physical assumptions, the most notable being that they assume the optimistic CE scenario and that case BB mass transfer is always unstable, whilst also using a simpler model for the Milky Way (see Appendix~\ref{sec:mw_changes}). Thus for better comparison we ran our simulation using model \modCaseBBOpt{} and the Milky Way model from \citet{Breivik+2020}. This results in 97, 101 and 43 detections for BHBHs, BHNSs and NSNSs respectively. Therefore, though we are in very good agreement for BHBHs, we predict much higher rates for BHNSs and NSNSs. These differences are likely due to using a different population synthesis code (COSMIC), which has different underlying physics assumptions from COMPAS. It is possible that the two codes handle NSs differently given our strong agreement for BHBHs.

\paragraph{\citet{Shao+2021}} most recently investigated the detectability binaries containing BHs in LISA using BSE and a relatively simple model for the Milky Way (assuming a uniform flat disc, constant star formation and a single metallicity). They assume that kicks for NSs formed through ECSN are slightly higher than our work ($50 \unit{km}{s^{-1}}$ instead of $30 \unit{km}{s^{-1}}$). This may account for their particularly low BHNS rate (as the binaries would be more likely to disrupt), which is a factor of 20 lower than ours, but we expect their assumption of the optimistic CE scenario, reduced Wolf-Rayet winds and lower SNR detection threshold would offset this. As we show in Appendix~\ref{sec:mw_changes}, their use of a simpler Milky Way model, especially with only a single metallicity, would lead to an overestimate of the BHBH and BHNS rates, which may explain the discrepancy in our results.
